\documentclass[11pt, a4paper]{article}

\author{Pierre-Marie DANIEAU, prld2\\prld2@kent.ac.uk}
\title{CO885 Proj. Res. : Workshop 5 - Find litterature}

\begin{document}

\maketitle

\begin{abstract}
Today's workshop goal is to find litterature and references for our project. My project is "Investigationg into methods for neurological disease".
To find usefull literrature, I'e looked on google scholar and found main references. Out of those paper I've looked if they were usefull or not, and then looked at their references to find better paper
\end{abstract}

\section{Keywords}

Since my project is "Investigating into methods for neurological disease" I had to find keywords for my research. The first one that came in my mind was "Neural disease" which lead me to find two other keywords : "Alzheimer" and "Parkinson". Those two disease lead me to a clever technology : The electroencephalogram.
By the end of it I had 4 keywords "neural disease", "Alzheimer", "Parkinson" and "Elecroencephalogram".

\section{The main papers : Google Scholar}

By looking on google scholar with neural "disease" I've found this article\cite{doi:10.1080/1071576031000083161} Which was cited 232 times and lead me to find Alzheimer and Parkinson.\\
Then I founded the article \cite{PRITCHARD1994118:1} who explained about EEG(i.e. electroencephalogram).
This document was related at this article by the website \cite{Debener11730:1} about the EEG
I found other but didn't had time to show them.

\bibliography{biblio}
\bibliographystyle{plain}

\end{document}